Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-09-06 parts/app.tex

The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
tendency to produce density profiles which were too shallow, resulting
typically in overestimates of the Einstein radius. Volunteers could
already set the size of the pixels by defining the radius of the lens
in pixels, with typical values between 8 and 12 pixels. Additionally,
it was possible to select smaller mass tiles in the central region,
thus allowing the mass profile to rise more steeply near the centre.
These options were was suggested as a possible cure.
\textcolor{red}{\bf IF: I don't even know what you mean by the last
  sentence: were those measures already implemented in the work
  described in that paper, or were these things considered a solution
  to the shallow profiles? Please clarify.}

>>>>

The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
tendency to produce density profiles which were too shallow, resulting
typically in overestimates of the Einstein radius. Allowing some extra
mass tiles in central region, thus allowing the mass profile to rise
more steeply near the centre, was suggested as a possible cure.
%\textcolor{red}{\bf IF: I don't even know what you mean by the last
%  sentence: were those measures already implemented in the work
%  described in that paper, or were these things considered a solution
%  to the shallow profiles? Please clarify.}
